### 2014-01-26 Papers_SVN/papers/rejected/2012/estimedia2012-dmec-mateus/tex/intro.tex
Versionando o meu mestrado.

% + Presents ME, remember it is widely used for video encoding, including H.264.
Motion Estimation (ME) is a technique used during video compression to explore temporal
redundancy in video sequences.
Temporal redundancy arises from the fact that neighboring frames often
share similar regions of pixels.
Therefore, the goal of ME is to \emph{estimate} the shifting of
such similar regions across neighbor frames, thus allowing for difference-based 
encoding.
%thus enabling them to be
%differentially encoded.
In block-based ME, the displacement of similar regions is represented by
\emph{motion vectors}, which are computed by
\emph{Block-Matching Algorithms} (BMAs).
Standards like the ISO MPEG series and the ITU-T H26x are examples of encoders
that use ME to improve the compression ratio of video streams~\cite{citeulike:1269699}.
In fact, about 90\% of the total encoding time in a H.264 encoder is spent in the
ME stage \cite{Yang:2005}.
Consequently, ME optimization is a relevant issue for H.264 and
video encoding in general.

@@

Many strategies have been proposed for ME optimization.
These strategies can be divided in three categories: 
algorithmic optimizations \cite{Ludwich:WebMedia:2011, SunNingning:TSS:2009, ShipingZhu:DS:2009};
parallelization of algorithms \cite{ChiaChunLin:PMRME:2007, HoyoungChang:HW:2009}; and
dedicated hardware implementations \cite{HaibingYin:HW:2010, HoyoungChang:HW:2009}.
The search for new methods to optimize the ME process is an important issue
to enable either the construction of real-time H.264 encoders or their implementation
in devices with limited computational resources, since these
optimizations aim to reduce ME complexity. 
Furthermore, the wide range of computer architectures available for the deployment of video encoders
spans a myriad of specific optimized implementations of encoding algorithms
\cite{ChiaChunLin:PMRME:2007, HoyoungChang:HW:2009, HaibingYin:HW:2010}. In such scenario, keeping a
homogeneous interface for encoding and 
decoding components allows the use of different optimized versions of algorithms (e.g. ME) 
without the need of modifying the whole encoder/decoder design, while maintaining compatibility
with video coding standards.

% Present our work as a solution for keeping interfaces
% Present our work as an ME optimization strategy based on picture partitioning
%  (parallel algorithms).
%  ...
In this paper, we show how a careful design process can be used 
to produce a ME component which has the same interface for different implementations.
Our \emph{Distributed Motion Estimation Component} (DMEC) uses an optimization strategy based on
picture partitioning, executing ME in parallel on distinct functional units.
In order to demonstrate the reusability provided by DMEC's interfaces, we provide implementations
using three distinct computer architectures: the Cell Broadband Engine (Cell BE), an Intel IA32 
Multicore Architecture, and a dedicated hardware generated using high-level synthesis (HLS).
All implementations of DMEC have the same interfaces and can be used
without modifications by an H.264 encoder. 
For each implementation of DMEC, we have evaluated the
encoding time and
objective  quality, which is measured by the Peak Signal-to-noise Ratio (PSNR).

% + paper structure(chapters' description)
The remaining of this paper are organized as follows:
Section~\ref{sota} makes an overview of issues and strategies for
ME optimization; % ?[and reviews techniques about designing for interfaces]
Section~\ref{dmec} presents DMEC and how it was designed;
Section~\ref{impl} describes the implementation of DMEC;
Section~\ref{eval} evaluates DMEC both in isolation and integrated with the standard
H.264 encoder;
Section~\ref{concl} closes the paper with our final considerations.

>>>>

% + Presents ME, remember it is widely used for video encoding, including H.264.
\IEEEPARstart{M}{otion} Estimation (ME) is a technique used to explore temporal
redundancy in video sequences during compression.
Temporal redundancy arises from the fact that neighboring frames often
share similar regions of pixels.
Therefore, the goal of ME is to \emph{estimate} the shifting of
such similar regions across neighbor frames, thus allowing for a difference-based 
encoding.
%thus enabling them to be
%differentially encoded.
In block-based ME, the displacement of similar regions is represented by
\emph{motion vectors}, which are computed by
\emph{Block-Matching Algorithms}.
Standards like the ISO MPEG series and the ITU-T H26x are examples of encoders
that use ME to improve the compression ratio of video streams~\cite{citeulike:1269699}.
In fact, about 90\% of the total encoding time in a H.264 encoder is spent in the
ME stage \cite{XiangLi:2004}, \cite{Yang:2005}.
Consequently, ME optimization is a relevant issue for H.264 and
video encoding in general.

@@

Many strategies have been proposed for ME optimization.
These strategies can be divided in three categories: 
algorithmic optimizations \cite{Ludwich:WebMedia:2011, SunNingning:TSS:2009, ShipingZhu:DS:2009};
parallelization of algorithms \cite{ChiaChunLin:PMRME:2007, HoyoungChang:HW:2009}; and
dedicated hardware implementations \cite{HaibingYin:HW:2010, HoyoungChang:HW:2009}.
The search for new methods to optimize the ME process is an important issue
to enable either the construction of real-time H.264 encoders or their implementation
in devices with limited computational resources, since these
optimizations aim to reduce ME complexity.

The wide range of computer architectures available for the deployment of video encoders
also spans a myriad of optimized implementations of encoding algorithms
\cite{ChiaChunLin:PMRME:2007, HoyoungChang:HW:2009, HaibingYin:HW:2010}. In such scenario, keeping a
homogeneous interface for encoding and 
decoding components allows for the use new optimized versions of algorithms (e.g. ME) 
without the need of modifying the whole encoder/decoder design and also maintaining compatibility
with video coding standards.

% Present our work as a solution for keeping interfaces
% Present our work as an ME optimization strategy based on picture partitioning
%  (parallel algorithms).
%  ...
In this paper, we show how a careful domain engineering design process can be used 
to produce a ME component which has the same interface for different implementations.
Our \emph{Distributed Motion Estimation Component} (DMEC) uses an optimization strategy based on
picture partitioning, executing ME in parallel on distinct functional units.
In order to demonstrate the reusability provided by DMEC's interfaces, we provide implementations
for three distinct computer architectures: the Cell Broadband Engine (Cell BE), an Intel IA32 
Multicore Architecture, and a dedicated hardware generated using high-level synthesis (HLS).
All implementations of DMEC have the same interfaces and can be used
without modifications by an H.264 encoder. 
For each implementation of DMEC we have evaluated the
encoding time and
objective  quality, which is measured by the Peak Signal-to-noise Ratio (PSNR).

% + paper structure(chapters' description)
The remaining of this paper are organized as follows:
Section~\ref{sota} makes an overview of issues and strategies for
ME optimization; % ?[and reviews techniques about designing for interfaces]
Section~\ref{dmec} presents DMEC and how it was designed;
Section~\ref{impl} describes the implementations of DMEC for Cell BE,
Multicore IA32, and dedicated hardware;
Section~\ref{eval} evaluates DMEC in isolation and integrated to the standard
H.264 encoder - JM;
Section~\ref{concl} closes the paper with our final considerations.

### 2014-01-26 Papers_SVN/papers/rejected/2012/sees2012-vhll_binding_generation-mateus/tex/eval.tex
Versionando o meu mestrado.

% ------------------------------------------------------------------------------
% NOTA TODO: Revisar / Reescrever esta subseção: Temperature Sensing
\subsection{Temperature Sensing}
The third case study is an application for temperature sensing.
This is a distributed application, composed by a \emph{Sensor} node which
measures the temperature and sends the obtained measures to a \emph{Sink} node
which receive the temperature values and process them.
The communication between the nodes is performed by radio on the context of a
\emph{Wireless Sensor Network} (WSN).

@@

In order to evaluate the performance of the generated native code adapters,
we have measured the time overhead for accessing the hardware mediators used by
the temperature sensing application.
Table \ref{tab:tempsensing_app_time_overhead_keso_epos_avr8} shows the
results for the AVR8 architecture using the KESO FFI.
Table \ref{tab:tempsensing_app_time_overhead_nanovm_epos_arm7} shows the
results for the ARM7 architecture using the NanoVM FFI.
For the temperature sensor device was measured the time of the \emph{sample}
method which samples the temperature from the environment.
For the NIC has measured the time for send an arbitrary message.
%
\begin{table*}[t]
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Method} & \textbf{Total ($\mu s$)} &
\textbf{Device ($\mu s$)} &
\textbf{Overhead (\%)}\\
\hline
\emph{Temp::sample} & 334.22 & 330 & 1.26 \\
\hline
\emph{NIC::send} & 8586.22 & 8580 & 0.072 \\
\hline
\end{tabular}
\caption{Time overhead generated by the native code adapters.
Architecture AVR8, KESO FFI.}
\label{tab:tempsensing_app_time_overhead_keso_epos_avr8}
\end{center}
\end{table*}
%
\begin{table*}[t]
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Method} & \textbf{Total ($\mu s$)} &
\textbf{Device ($\mu s$)} &
\textbf{Overhead (\%)}\\
\hline
\emph{Temp::sample} & 946.04 & 942 & 0.43 \\
\hline
\emph{NIC::send} & 958.39 & 950 & 0.87 \\
\hline
\end{tabular}
\caption{Time overhead generated by the native code adapters.
Architecture ARM7, NanoVM FFI.}
\label{tab:tempsensing_app_time_overhead_nanovm_epos_arm7}
\end{center}
\end{table*}
%
%
The ``Total'' time and the ``Device'' time from the two tables are not
comparable, since they are obtained from distinct platforms.
However, the overhead value is, and it is less than 1.3\% for all devices.
The time overhead generated by NanoVM should be bigger than in KESO JVM because
NanoVM has an overhead for interpreting the \java~bytecode.
KESO JVM does not have this kind of overhead since all bytecode is translated
to C and then to native code.
However, this is not seen comparing the tables because the bytecode
interpretation overhead was not measured for NanoVM.
The measure overhead from NanoVM comes specifically from the native method,
which uses ``push'' and ``pop'' operations to interact with NanoVM stack for
obtaining the method's arguments and for returning the method's results.

% ------------------------------------------------------------------------------

>>>>

% ------------------------------------------------------------------------------
\section{Cases study} \label{sec:eval}
This section presents the evaluation of the proposal to interface hardware
devices and embedded VHLL, introduced at Section \ref{sec:proposal}, on the
context of embedded \java~and embedded \lua.
In order to evaluated our proposal three cases study are presented: serial
communication, distributed motion estimation, and temperature sensing.
The proposal was evaluate according to the following metrics: performance,
memory consumption, platform portability, developer support, and reuse of
native code adapters among distinct FFIs.

\subsection{Serial Communication}
% NOTA:  Acho que é interessante citar os meus papers anteriores IADIS AC 2011.
% Algo como, resultados iniciais mostrados para KESO em \cite...
The first case study evaluated as a synthetic application which uses the
\emph{Universal Asynchronous Receiver Transmitter} (UART) hardware device for
serial communication.
Such application, was evaluated in \java, using the KESO FFI, for the
architectures IA32, AVR8, and PPC32.
The Figure \ref{progjava:uart_app} shows the \java~source of the application,
which uses the UART hardware mediator in order to write characters on a serial
device.

\progjava{uart_app}{UART application.}

The \java~ class \emph{UART}, generated as one of the outputs of EBG, is the
\java~counterpart of the UART hardware mediator and has only native methods
without implementation.
The other output of EBG is the native code adapter already tailored to be
integrated with the KESO JVM.
This integration process is show in details in our previous work
\cite{Ludwich:IADIS_AC:2011}.
At such work the UART application using our approach is compared to the a
equivalent application written using the \emph{Java Standard Edition} platform,
which uses the \emph{Java Native Interface} (JNI) as FFI, running on Linux.
Our approach is around 38X faster than using JNI and Linux.

\subsection{Distributed Motion Estimation}
% Dizer que nosso trabalho anterior mostra a versão em Java feita a mão?
% Dizer que neste trabalho a versão Java foi automaticamente gerada e mostrar a
% versão em Lua.
The second case study for the proposed method is a real application which uses
a component to perform \emph{Motion Estimation} (ME) for H.264 video encoding.
In this case study we have generated native code adapters for \java~and \lua.
Such component for ME computation was developed for the project the Brazilian
project ``Rede H.264'', which aims to develop standards and products for the
Brazilian Digital Television \cite{RedeH264:2009}.

Motion Estimation is a technique used to explore the similarity between
neighboring frames in a video sequence, thus enabling them to be differentially
encoded, improving the compress ratio of the generated bitstream
\cite{citeulike:1269699}.
ME is a significant stage for H.264 encoding, since it consumes around 90\% of
the total time of the encoding process \cite{XiangLi:2004}.
In order to improve the performance of ME, the component uses a data
partitioning strategy where the motion estimation for each partition of the
picture is performed in parallel in a specific functional unit, such as a core
of a multicore processor.

% O DMEC é implementado como um componente em C++ e é exportado para a
% \textit{VHLL}
% alvo desenvolvendo-se um adaptador de código nativo para cada objeto sendo
% abstraído.

Our previous work shows handmade native code adapters for KESO
JVM \cite{Ludwich:IADIS_AC:2011}.
In the present work we have used the EBG to generate the same adapter for KESO
JVM and also an adapter for the LuaVM.
In the case of \lua~the native code adapter is a C code using the FFI of \lua~
that is ready to be used.
In the case of KESO JVM the native code adapter is a \emph{weavelet}
class, which is used during the KESO generation process, generating the final
native code adapter.

In order to test the ME component we wrote an application with mimics the
behavior of an H.264 encoder, it provides the component with pictures, get from
the component the ME results (motion vectors and motion cost), and checks if
the results are correct.
The Figure \ref{progjava:dmec_java_app} shows the Java version of the
application, and the Figure \ref{proglua:dmec_lua_app} shows the same
application written in \lua.

\progjava{dmec_java_app}{ME Java application.}

\proglua{dmec_lua_app}{ME Lua application.}

% \multprogjavatwoh{dmec_java_app}{dmec_lua_app}{ME Java and Lua applications.}

\subsection{Temperature Sensing}
The third case study is an application for temperature sensing.
This is a distributed application, composed by a \emph{Sensor} node which
measures the temperature and sends the obtained measures to a \emph{Sink} node
which receive the temperature values and process them.
The communication between the nodes is performed by radio on the context of a
\emph{Wireless Sensor Network} (WSN).

@@

In order to evaluate the performance of the generated native code adapters,
we have measured the time overhead for accessing the hardware mediators used by
the temperature sensing application.
Table \ref{tab:tempsensing_app_time_overhead_keso_epos_avr8} shows the
results for the AVR8 architecture using the KESO FFI.
Table \ref{tab:tempsensing_app_time_overhead_nanovm_epos_arm7} shows the
results for the ARM7 architecture using the NanoVM FFI.
For the temperature sensor device was measured the time of the \emph{sample}
method which samples the temperature from the environment.
For the NIC has measured the time for send an arbitrary message.
%  
\begin{table}[t]
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Method} & \textbf{Total ($\mu s$)} &
\textbf{Device ($\mu s$)} &
\textbf{Overhead (\%)}\\
\hline
\emph{Temp::sample} & 334.22 & 330 & 1.26 \\
\hline
\emph{NIC::send} & 8586.22 & 8580 & 0.072 \\
\hline
\end{tabular}
\caption{Time overhead generated by the native code adapters.
Architecture AVR8, KESO FFI.}
\label{tab:tempsensing_app_time_overhead_keso_epos_avr8}
\end{center}
\end{table}
% 
\begin{table}[t]
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Method} & \textbf{Total ($\mu s$)} &
\textbf{Device ($\mu s$)} &
\textbf{Overhead (\%)}\\
\hline
\emph{Temp::sample} & 946.04 & 942 & 0.43 \\
\hline
\emph{NIC::send} & 958.39 & 950 & 0.87 \\
\hline
\end{tabular}
\caption{Time overhead generated by the native code adapters.
Architecture ARM7, NanoVM FFI.}
\label{tab:tempsensing_app_time_overhead_nanovm_epos_arm7}
\end{center}
\end{table}
% 
%
The ``Total'' time and the ``Device'' time from the two tables are not
comparable, since they are obtained from distinct platforms.
However, the overhead value is, and it is less than 1.3\% for all devices.
The time overhead generated by NanoVM should be bigger than in KESO JVM because
NanoVM has an overhead for interpreting the \java~bytecode.
KESO JVM does not have this kind of overhead since all bytecode is translated
to C and then to native code.
However, this is not seen comparing the tables because the bytecode
interpretation overhead was not measured for NanoVM.
The measure overhead from NanoVM comes specifically from the native method,
which uses ``push'' and ``pop'' operations to interact with NanoVM stack for
obtaining the method's arguments and for returning the method's results.
